\documentclass[10pt]{article}

\usepackage{lipsum}
\usepackage{url}
\usepackage{float}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{rotating}
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[numbered]{matlab-prettifier}

\newcommand{\documentTitle}{Lab 3 - Basic Circuits}
\newcommand{\documentAuthor}{Andrew Pham, Aneel Damaraju}
\newcommand{\courseTitle}{ELEC 240}
\newcommand{\testDate}{September 19,2018}
\newcommand{\reportDate}{September 26, 2018}

\geometry{margin=1in}
\lstset{
    tabsize=4,
    basicstyle={\ttfamily},
    captionpos=b,
    belowskip=1em,
    aboveskip=1em,
    numbers=left,
	escapechar=\@,
}

\title{
    \textbf{\courseTitle} \\
    \textbf{\documentTitle} \\
    \bigskip
    \textbf{\large{Test performed: \testDate}} \\
    \textbf{\large{Report submitted: \reportDate}} \\
    \bigskip
    \bigskip
}
\author{\documentAuthor}
\date{}

\begin{document}

\maketitle

\newpage

\section{Objective}

In this lab, we explored Kirchoff's laws, and transfer functions through the use of various circuit elements, such as potentiometers, and software, such as LT Spice

\medskip

\textit{Note (To be deleted): Think of this test report as a document with your peers as your readers. This means you can assume a similar knowledge background as you. Your readers should be able to easily understand what is going on, and also be able to repeat your lab results based on your document and all references you cite.}

\textit{For the Objective section, identify the test you performed and its objectives. The objectives of the test are important to state because they are usually analyzed in the conclusion to determine whether the test succeeded.}

\section{Materials}

Your text here

\medskip

\textit{Note (To be deleted): Provide a bullet point list of components, software tools, and hardware (such as the NI VirtualBench or DMM) used during the lab}

\section{Test Description}

Your text here

\medskip

\textit{Note (To be deleted): This section provides a summary of the test your team performed. Give enough information so readers can understand what you did, but do not go into the details of every step.}

\subsection{Pre-Lab Calculations and Schematics}

Your text here

\medskip

\textit{Note (To be deleted): Include the homework pre-calculations and schematics that serve as the initial setup for the test. Briefly explain the importance of each item you include. You may want to number your equations/figures so you can refer to them in later sections. Including photos of handwritten work is okay.}

\section{Results and Discussion}

\subsection{Experiment 3.1: Resistive Voltage Dividers}
\subsubsection{Part A}

	 The voltage reading on the DMM by a 2$V_{pp}$ sine wave is $.704 V_rms$, or .704 $V_in$. The voltage reading on the DMM for a similar square wave is 1.096 $V_in$. Then, readings were done for various frequencies for the same value sine wave as used in the initial test. The results were as follows
\begin{itemize} 
	\item 5 Hz		.641V
	\item 50 Hz		.701V
	\item 500 Hz	.701V
	\item 5 kHz		.49V
	\item 50 kHz	0V
\end{itemize}
	It seems that the appropriate frequency for the DMM is 50-500 Hz to be safe, but more reasonably 10Hz-1kHz.
\subsubsection{Part B}
	 The voltage divider ratio should be $\frac{10,(10+10)} = ½ V_in$  for two 10 kOhm Resistors in series. For the sine wave, the output is $.351 V_ac$, which is 49\% of the initial Voltage, consistent with the voltage divider equation 
	 At 47 Ohms the $V_out = .243$, which is inconsistent, with the voltage divider equation, indicating that the voltmeter may have inconsistent readings at low voltages. 
	 At 1MOhm the output voltage is .335, indicating that there may be a range of acceptable resistance for the voltmeter, just like we noted an acceptable frequency range.
\subsubsection{Part C} 
	Using the same sine wave, but wih 100 Hz, the potentiometer is connected in series and the voltage drop across it is recorded. At the midpoint, $V_out = .386 or .55 V_in$ this value is reasonable within error for such an analog device. 
	The values of the output voltage at different divisions are given below.
	\begin{itemize}
		\item 1 -.76V
		\item 2 -.653V
		\item 3 -.589V
		\item 4 -.506V
		\item 5 -.389V
		\item 6 -.273V
		\item 7 -.181V
		\item 8 -.076V
		\item 9 -0.002V
		\item 10-0.0V
	\end{itemize}
 	It seems as if the values were evenly spaced as if they're were only 9 divisions, since the 9th and 10th both had 0V out.
\subsection{Experiment 3.2: Filters and Transfer Function}
\subsection{Part A}
	Measuring the frequency and the amplitude of the output voltage across an RC circuit. The values recorded can be seen below
\begin{table}[H]
\begin{center}
	\caption{Frequency and the amplitude of the output voltage across an RC circuit}
	\label{tab: 32A}
	   \begin{tabular}{l|c|r}
		\textbf{Frequency} & \textbf{Voltage} & \textbf{Phase shift}\\
		(Hz) & (V) & (ms) \\
		\hline
		20 & .99 & 1.97\\
		50 & .96 & 1.02\\
		100 & .88 & .869\\
		200 & .68 & .632\\
		500 & .39 & .402\\
		1k & .16 & .227\\
		2k & .065 & .119\\
		5k & .041 & .046\\
		10k & .021 & .023\\
		20k & .010 & .012\\
	\end{tabular}
\end{center}
\end{table}

These results from Table \ref{tab: 32A} were then used plotted onto Figure \ref{fig: 32A5}, using MATLAB. When compared to the values of Figure \ref{fig: 32A6} it can be seen that the experimental results match up with the actual results, confirming the transfer function of AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA

\subsubsection{Part B}

The screenshot of the LT spice AC analysis of an RC circuit can be seen in figure \ref{simpleRC}, The gain at low frequencies is 0 dB or 1 V/V. The cutoff frequency happens at approx. 250 Hz. At high frequencies the gain rolloff becomes almost linear, with a slope of -1 dB/dec. At low frequencies, the phase is $0\deg$ or in phase. At high frequencies the phase is $-90\deg$. This is because a capacitor will ideally lag in voltage when put in a circuit in series, and at low frequencies the capacitor acts more like a resistor.

After adding the  


\section{References}

Your text here

\medskip

\textit{Note (To be deleted): List any datasheets, websites, lab procedure, etc. used during the lab.}

\section{Conclusion}

Your text here

\medskip

\textit{Note (To be deleted): While the ``Results and Discussion'' section focused on the test results individually, the ``Conclusion'' discusses the results in the context of the entire experiment. Usually, the objectives given in the ``Introduction'' are reviewed to determine whether the experiment succeeded. If the objectives were not met, you should analyze why the results were not as predicted.}

\section{Errors}

Your text here

\medskip

\textit{Note (To be deleted): Briefly list sources of error and discuss how to eliminate or deal with them}

\end{document}
